---
title: "WUP_04"
author: "iboni archie"
date: "summer 2021"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

```{r}
gssdata=read_csv("GSScsv.csv")
```



# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
basicCN <- ggplot(gssdata,aes(x=DEGREE,y=WORDSUM))
```



## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

In this box plot we see that the LT High school plot is lower than the plots   
for   Bachelor, Graduate and Junior college. You can slide the LT high school   under each of those three and see a significant difference.    


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(WORDSUM~DEGREE,data=gssdata)
```

In the graph above we see median of the of the people who got degree compared     
people who only completed LT High school. LT High school mean is a 7 and the     
Bachelor and Graduate is at 9 and 10.This is showing that people who got high   degree recived higher scores on the WORDSUM test.    

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
model1 <- aov(WORDSUM~DEGREE,data=gssdata)
summary.aov(model1)
```


```{r}
plot(TukeyHSD(model1))
```


```{r}
model1 <- aov(WORDSUM~DEGREE,data=gssdata)
summary.aov(model1)
```
```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 13.2, 2, 2))
plot(TukeyHSD(model1),las=2)
```


In this graph it gives us a clear picture of the degrees with a significant   difference between the two.Anything that the dotted line does not pass through  means that there is a difference between the numbers which are HIGH SCHOOL and JUNIOR COLLEGE, LT HIGH SCHOOL and GRADUATE and HIGH SCHOOL and GRADUATE.That   shows that higher degrees recieved higher scores than No Degrees.    



# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
